Experimental and numerical studies of the effects of resonant and random excitations of the proton beam in the LHC, with applications to the design of a pulsed hollow electron lens for active halo control

### 2018-02-21 resex.tex
bibliography is fixed
Removed package siunitx. Started revision of Section III on residual kicks.

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{color}
\usepackage{siunitx}
\usepackage{url}

@@

\section{Sources of residual field in the proton beam core region and first order estimates\label{sec:core}}
With the current HEL layout as shown in Fig.~\ref{fig:hel_layout}, parasitic kicks on the proton beam core can arise in the central region due to profile imperfections in the electron beam and at the entrance and exit of the HEL, where electron and proton beam overlap. Currently, no HEL is installed in the LHC, and the kick on the proton beam core must therefore be emulated with the help of other devices already installed in the LHC. For this purpose the kick is approximated to first order by a dipole kick. During the experiments presented in this paper, the dipole kick with the corresponding excitation pattern could then be applied with the LHC transverse damper as will be described in detail in Section~\ref{sec:adt}. As will be shown in Sec.~\ref{core:sec:1} and \ref{core:sec:2}, the expected kick to first order from the HEL bends is estimated to be~(Eq.~\ref{eqn:kick_bends}):
\begin{equation}
	\Delta x'_{\rm{bends}},\Delta y'_{\rm{bends}}\approx \SI{0.5}{nrad},
\end{equation}
and for the central region due to profile imperfections~(Eq.~\ref{eqn:kick_central}):
\begin{equation}
	\Delta x'_{\rm{central \ region}}, \Delta y'_{\rm{central \ region}} \approx \SI{20}{nrad} % this should be rounded to the same number of digits as the 0.5nrad
\end{equation}
where the current HEL design parameters are used (see Table~\ref{tab:hllhc_param}--\ref{tab:hel_param}). The contribution from the central region is clearly dominating.

\subsection{Uncompensated kicks from HEL bends}
\label{core:sec:1}
As reference for the estimate of the dipole component originating from the HEL bends, the symplectic map derived in \cite{hel_bends_stancari} is used. In this case the HEL bends are modeled as a bent cylindrical pipe with a static charge distribution of 1~A and 5~keV electrons deflected in the horizontal plane, where the parameters were her still based on the old gun design for the Tevatron electron lens \textcolor{red}{Giulio, is this correct?}. In case of an U-shaped HEL, the transverse dipole kicks at entrance and exit add up, while for a S-shape the kicks compensate each other. For this reason a S-shape has been chosen for the HL-LHC HEL (see Fig.~\ref{fig:hel_layout}). Assuming and S-shaped HEL, uncompensated kicks therefore only arise from imperfections, which can originate from profile imperfections and current fluctuations. As a first estimate, we assume in this paper 10\% fluctuations between the entrance and exit and, in addition, that the kicks from entrance and exit due to these imperfections add up. Using the electric field calculations in \cite{hel_bends_stancari}, the maximum values for the integrated electric field are then
\begin{equation}
\int_{z_1}^{z_2} E_{x,y} dz= 10 \ \mathrm{kV}.
\end{equation}
%given an \SI{1}{A}, \SI{5}{keV} electron beam.
%For \SI{7}{TeV} protons and neglecting magnetic effects, this yields a kick of:
%\begin{equation}
%\Delta x'=\Delta y'= \SI{1.4}{nrad},
%\end{equation}
%Scaling to the HEL design parameters of a \SI{5}{A} and \SI{10}{keV} electron beam (Table~\ref{tab:hel_param}), one obtains:
%\begin{equation}
%\int_{z_1}^{z_2} E_{x} dz= 36 \ \mathrm{kV} \Rightarrow \Delta x'= \q{5.1}{nrad}
%\end{equation}
Neglecting magnetic effects and scaling to HL-LHC and HEL design parameters (Tables~\ref{tab:hllhc_param}--\ref{tab:hel_param}) yields a kick of \cite{md_sim_hel_res_ex_fitterer}:
\begin{equation}
\int_{z_1}^{z_2} E_{y} dz= 36 \ \mathrm{kV} \Rightarrow \Delta y'= \q{5.1}{nrad}
\end{equation}
Assuming now 10\% fluctuation between entrance and exit kick, the expected kick from the HEL bends is
\begin{equation}\label{eqn:kick_bends}
\Delta x', \Delta y'\approx \q{0.5}{nrad}.
\end{equation}

@@

\begin{equation}
  \label{eqn:kick_central}
  \Delta x'_{\rm{central \ region}}, \Delta y'_{\rm{central \ region}} = \SI{20}{nrad}.
\end{equation}

>>>>

\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{hyperref}% add hypertext capabilities
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{color}
%\usepackage{siunitx}
\usepackage{url}

@@

\section{Sources and estimates of residual fields}
\label{sec:core}

Parasitic kicks on the proton beam core can be due to electron-beam
profile imperfections in the overlap region, or to the injection and
extraction toroidal bends, where electrons and protons overlap, as
shown in the layout of Fig.~\ref{fig:hel_layout}.

Currently, no HEL is installed in the LHC, and the kick on the proton beam core must therefore be emulated with the help of other devices already installed in the LHC. For this purpose the kick is approximated to first order by a dipole kick. During the experiments presented in this paper, the dipole kick with the corresponding excitation pattern could then be applied with the LHC transverse damper as will be described in detail in Section~\ref{sec:adt}. As will be shown in Sec.~\ref{core:sec:1} and \ref{core:sec:2}, the expected kick to first order from the HEL bends is estimated to be~(Eq.~\ref{eqn:kick_bends}):
\begin{equation}
	\Delta x'_{\rm{bends}},\Delta y'_{\rm{bends}}\approx \q{0.5}{nrad},
\end{equation}
and for the central region due to profile imperfections~(Eq.~\ref{eqn:kick_central}):
\begin{equation}
	\Delta x'_{\rm{central \ region}}, \Delta y'_{\rm{central \ region}} \approx \q{20}{nrad} % this should be rounded to the same number of digits as the 0.5nrad
\end{equation}
where the current HEL design parameters are used (see Table~\ref{tab:hllhc_param}--\ref{tab:hel_param}). The contribution from the central region is clearly dominating.

\subsection{Uncompensated kicks from HEL bends}
\label{core:sec:1}
As reference for the estimate of the dipole component originating from the HEL bends, the symplectic map derived in \cite{hel_bends_stancari} is used. In this case the HEL bends are modeled as a bent cylindrical pipe with a static charge distribution of 1~A and 5~keV electrons deflected in the horizontal plane, where the parameters were her still based on the old gun design for the Tevatron electron lens \textcolor{red}{Giulio, is this correct?}. In case of an U-shaped HEL, the transverse dipole kicks at entrance and exit add up, while for a S-shape the kicks compensate each other. For this reason a S-shape has been chosen for the HL-LHC HEL (see Fig.~\ref{fig:hel_layout}). Assuming and S-shaped HEL, uncompensated kicks therefore only arise from imperfections, which can originate from profile imperfections and current fluctuations. As a first estimate, we assume in this paper 10\% fluctuations between the entrance and exit and, in addition, that the kicks from entrance and exit due to these imperfections add up. Using the electric field calculations in \cite{hel_bends_stancari}, the maximum values for the integrated electric field are then
\begin{equation}
\int_{z_1}^{z_2} E_{x,y} dz= 10 \ \mathrm{kV}.
\end{equation}
%given an \q{1}{A}, \q{5}{keV} electron beam.
%For \q{7}{TeV} protons and neglecting magnetic effects, this yields a kick of:
%\begin{equation}
%\Delta x'=\Delta y'= \q{1.4}{nrad},
%\end{equation}
%Scaling to the HEL design parameters of a \q{5}{A} and \q{10}{keV} electron beam (Table~\ref{tab:hel_param}), one obtains:
%\begin{equation}
%\int_{z_1}^{z_2} E_{x} dz= 36 \ \mathrm{kV} \Rightarrow \Delta x'= \q{5.1}{nrad}
%\end{equation}
Neglecting magnetic effects and scaling to HL-LHC and HEL design parameters (Tables~\ref{tab:hllhc_param}--\ref{tab:hel_param}) yields a kick of \cite{md_sim_hel_res_ex_fitterer}:
\begin{equation}
\int_{z_1}^{z_2} E_{y} dz= 36 \ \mathrm{kV} \Rightarrow \Delta y'= \q{5.1}{nrad}
\end{equation}
Assuming now 10\% fluctuation between entrance and exit kick, the expected kick from the HEL bends is
\begin{equation}\label{eqn:kick_bends}
\Delta x', \Delta y'\approx \q{0.5}{nrad}.
\end{equation}

@@

\begin{equation}
  \label{eqn:kick_central}
  \Delta x'_{\rm{central \ region}}, \Delta y'_{\rm{central \ region}} = \q{20}{nrad}.
\end{equation}
